Rank Recovery

### 2020-11-13 output_scripts/rank_recovery.Rmd
update rank recovery with real data from isi_predict

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE)
library(here)
library(tidyverse)
library(rstan)
library(cmdstanr)
library(compete)
library(posterior)
```

@@

```{r prop full recover}
all_sims$sim <- rep(1:20, each = 5)

@@

@@

```{r check isi function, results='hide'}
clean_sim_data <- readRDS(file = here("output", "rank_sims", 
                                        "rmd_stan",
                                        "sim_data_M3.RDS"))
clean_sim_data_dc$N_count

@@

compute_isi(count_data_dc, curr_ranking = c(5,3,1,2,4))

@@

agg_rank_train <- order(agg_train_mean_rank)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE)
library(here)
library(tidyverse)
library(rstan)
library(cmdstanr)
library(compete)
library(posterior)

theme_set(theme_minimal())
```

@@

```{r prop full recover}
all_sims$sim <- rep(1:50, each = 5)

@@

Similarly, we can summarise this by
computing the Spearman rank correlation between each of these 
models and the truth. The C-MMHP model unsurprisingly best recovers the
true rankings, with the I&SI model performing similarly.

```{r analyse sims}
sim_files <- list.files(here("output","rank_sims","sims_m3_dc_isi"))

all_sims <- list()
for(i in seq_along(sim_files)) {
 single_fit <- readRDS(here("output", "rank_sims", 
                            "sims_m3_dc_isi",
                            sim_files[i]))
 all_sims[[i]] <- single_fit
}

spear <- function(sim_data) {
  truth <- sim_data$truth
  sim_data %>%
    select(m1:isi) %>%
    map( ~cor.test(truth, .x,
                   method = "spearman")$estimate  ) %>%
    enframe() %>%
    unnest(cols = c(value))
}

sim_data <- map_dfr(all_sims, spear)

name <- sim_data$name

sim_data$name <- case_when(
          name == "isi" ~ "I&SI",
          name == "m1" ~ "C-HP",
          name == "m2" ~ "C-DCHP",
          name == "m3_dc" ~ "C-MMHP")

sim_data$name <- factor(sim_data$name, levels = c("I&SI","C-HP",
                                                  "C-DCHP", "C-MMHP"))

sim_data %>% 
  rename(Method = name, corr = value) %>%
  ggplot(aes(Method,corr)) + geom_boxplot() +
  labs(y = "Rank Correlation")
  # in a nice long format

@@

```{r check isi function, results='hide'}
clean_sim_data <- readRDS(file = here("output", "rank_sims", 
                                        "rmd_stan",
                                        "sim_data_M3_dc.RDS"))
clean_sim_data_dc$N_count

@@

compute_isi(count_data_dc, curr_ranking = c(2,5,4,1,3))

@@

# for highest to lowest
agg_rank_train <- rev(order(agg_train_mean_rank))
```

@@

## Real Data

To be completed.

```{r plot isi scores}
sim_files <- list.files(here("output","rank_sims","predict_isi"))

all_sims <- list()
for(i in seq_along(sim_files)) {
  single_fit <- readRDS(here("output", "rank_sims", 
                             "predict_isi",
                             sim_files[i]))
  all_sims[[i]] <- single_fit
}

cohort_scores <- all_sims %>%
  map(~as_tibble(.)) %>%
  bind_rows(.id="index")

cohort_scores %>% 
  mutate(ISI = I_score + SI_score) %>%
  ggplot(aes(model,ISI)) + geom_boxplot()
```
